### 2016-03-15 paper/stereo.tex
figure 2

We compare SF against competing approaches over three problems in
Computer Vision, specifically, stereo, optical flow, and layered
depthmap estimation.

>>>>

We compare SF against competing approaches over three problems in
Computer Vision, specifically, stereo, optical flow, and layered
depthmap estimation (see Fig.~\ref{fig:problem}).
